---
title: ''
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

#Load packages
library(tidyverse)
library(lubridate)
library(readxl)
library(janitor)
library(keyring)

#For reference
dataDictionary <- read_excel("Data Dictionary.xlsx")

```

Run chunks for each provider when testing data is received to produce a standard format to import into the selenium script. Then run final chunk to combine all data.

Notes: 

* For variables with INEDSS_Expected_Values listed, cleaned data must be formatted to values listed. First letters are acceptable substitutes if unique (e.g. M / F /U for Male, Female, Unknown) 

* All date variables must be of class "Date" after cleaning.

* Code currently only expecting one value listed for race. Will need additional coding in all scripts if site sends multiple values.

*Currently no coding in selenium scripts to enter "Communicates in English", "Primary Language", and "Onset Date", because not sure if any sites will actually be able to provide this. Variables exist in the cleaning so will be easy to add to selenium scripts later if other sites can provide.



```{r physicians_immediate_care}

#key_set("pic_contact_first")
#key_set("pic_contact_last")
#key_set("pic_contact_phone")

#Catch-up file
# cases_pic <- read_excel("Test Data/PIC/Cook_ALL_FORMAT.xlsx") %>%
#   rename_all(tolower) %>%
#   rename(specimenCollectionDate = svc_date,
#          address = address1,
#          phone = pat_phone,
#          phone2 = cell_phone,
#          orderingProvider = `ordering provider`
#          ) %>%
#   filter(itemresults == "Positive"  & labcompanyname != "Quest") %>%  
#   filter(!(city %in% c("SKOKIE", "EVANSTON", "OAK PARK", "STICKNEY", "CHICAGO"))) %>%
#   mutate(orderingFacility = paste('Physicians Immediate Care', clinic, sep = "-"),
#          dob = excel_numeric_to_date(birthdate),
#          firstName = str_to_title(first_name),
#          lastName = str_to_title(last_name),
#          reporterFirst = key_get("pic_contact_first"),
#          reporterLast = key_get("pic_contact_last"),
#          reporterPhone = key_get("pic_contact_phone"),
#          reporterOrganizationName = "Physicians Immediate Care",
#          state = state.name[match(state,state.abb)],
#          orderingProviderLast = str_extract(orderingProvider, "[^,]+"),
#          orderingProviderFirst = str_extract(orderingProvider, '\\b[^,]+$'),
#          orderingProviderFirst = ifelse(nchar(orderingProviderFirst < 2), NA, orderingProviderFirst)
#          )%>%
#   mutate(earliestReportDate = as.Date(specimenCollectionDate)) %>%  
#   #Catch up document sent on 4/28 but will use specimen date here, otherwise will create a misleading false peak in our epicurve
#   select(one_of(dataDictionary$Variable))


#Files going forward
date_extension <- paste(month(Sys.Date() - 5),day(Sys.Date() - 5), sep = ".")

cases_pic <- read_excel(paste0("Test Data/PIC/Cook ", date_extension,".xlsx")) %>%
  rename_all(tolower) %>%
  rename(specimenCollectionDate = svc_date,
         address = address1,
         phone = pat_phone,
         phone2 = cell_phone,
         orderingProvider = `ordering provider`,
         dob = birthdate
         ) %>%
  filter(itemresults == "Positive"  & labcompanyname != "Quest") %>%  
  filter(!(city %in% c("SKOKIE", "EVANSTON", "OAK PARK", "STICKNEY", "CHICAGO"))) %>%
  filter(county == "Cook") %>%
  mutate(orderingFacility = paste('Physicians Immediate Care', clinic, sep = "-"),
         #dob = excel_numeric_to_date(birthdate),
         firstName = str_to_title(first_name),
         lastName = str_to_title(last_name),
         reporterFirst = key_get("pic_contact_first"),
         reporterLast = key_get("pic_contact_last"),
         reporterPhone = key_get("pic_contact_phone"),
         reporterOrganizationName = "Physicians Immediate Care",
         state = state.name[match(state,state.abb)],
         orderingProviderLast = str_extract(orderingProvider, "[^,]+"),
         orderingProviderFirst = str_extract(orderingProvider, '\\b[^,]+$'),
         orderingProviderFirst = ifelse(nchar(orderingProviderFirst < 2), NA, orderingProviderFirst)
         )%>%
  mutate(earliestReportDate = Sys.Date() - 4) %>%  #Generally will be Sys.Date but set manually to email date if not running same day 
  select(one_of(dataDictionary$Variable))


```

```{r final}

#Create preferred structure of output
cases_blank <- dataDictionary %>%
  filter(is.na(Default_Value) | (INEDSS_Section == 'Reporting Source' & Variable != "reporterComment")) %>%
  select(Variable) %>%
  mutate(value = NA) %>%
  pivot_wider(names_from = Variable, values_from = value) %>%
  filter(!is.na(firstName))

#Re-write preferred structure to repository whenever updated
#write_csv(cases_blank, "Expected Data Structure.csv")


#Merge all cleaned files and remove out of state cases
testData <- mget(ls(pattern="^cases.*")) %>%   
  bind_rows() %>%
  mutate(labReportDate = as.Date(specimenCollectionDate)) %>%
  mutate(dateLHDReceived = as.Date(earliestReportDate)) %>%
  mutate_at(vars(ethnicity, race), ~ifelse(is.na(.), "Unknown", .)) %>%
  mutate(address2 = str_remove_all(address2, "#")) %>%  #Address must be alphanumeric
  mutate(county = str_to_title(county)) %>% #Format to match INEDSS
  filter(state == "Illinois")

#Write data to csv
write_csv(testData, 'testData.csv', append = F)

```


